MADA Project Part 2

### 2024-03-04 R/processing-code/MADAproject_pt2_ruiz.qmd
Part 2 Render correction
located source of error preventing the qmd from rendering.

#Combine the datasets
combined_data <- bind_rows(data_list)

@@

# Save the combined data frame as a CSV file
write.csv(combined_data, combined_path, row.names = FALSE)

# View the first few rows to confirm it's loaded correctly
head(virus_data)
```

@@

#load the first few rows of data to verify the data loaded as expected
head(cases_vet)
#date of onset is missing for some records, however, they are not needed for this project.

@@

```{r}
earliest_date <- min(mosquito_raw$`Collection Date`, na.rm = TRUE)
latest_date <- max(mosquito_raw$`Collection Date`, na.rm = TRUE)
print(paste("Date range:", earliest_date," to ", latest_date))
```

@@

# Prepare virus_data: Find the first positive EEE test date by year
first_positive_eee_test_by_year <- virus_data %>%
  filter(Virus == "EEE") %>%
  mutate(Year = year(as.Date(Collection.Date))) %>%
  group_by(Year) %>%
  summarise(First_Positive_Test_Date = min(Collection.Date)) %>%
  ungroup() %>%
  arrange(Year)

@@

```{r}
eee_positive_by_county <- virus_data %>%
  filter(Virus == "EEE") %>%  # Filter for rows where Virus is EEE
  group_by(County) %>%
  summarise(EEE_Positive_Tests = n()) %>%  # Count the number of EEE positive tests in each group
  arrange(desc(EEE_Positive_Tests))  # Order the results by EEE_Positive_Tests in descending order

>>>>

#Combine the datasets
combined_virus_data <- bind_rows(data_list)

@@

# Save the combined data frame as a CSV file
write.csv(combined_virus_data, combined_path, row.names = FALSE)

# View the first few rows to confirm it's loaded correctly
head(combined_virus_data)
```

@@

#load the first few rows of data to verify the data loaded as expected
head(cases_vet)
#date of onset is missing for some records, however, they are not needed for this project. 
```

@@

```{r}
earliest_date <- min(mosquito_raw$`collection date`, na.rm = TRUE)
latest_date <- max(mosquito_raw$`collection date`, na.rm = TRUE)
print(paste("Date range:", earliest_date," to ", latest_date))
```

@@

# Prepare virus_data: Find the first positive EEE test date by year
first_positive_eee_test_by_year <- combined_virus_data %>%
  filter(Virus == "EEE") %>%
  mutate(Year = year(as.Date(`Collection Date`))) %>%
  group_by(Year) %>%
  summarise(First_Positive_Test_Date = min(`Collection Date`)) %>%
  ungroup() %>%
  arrange(Year)

@@

```{r}
eee_positive_by_county <- combined_virus_data %>%
  filter(Virus == "EEE") %>%  # Filter for rows where Virus is EEE
  group_by(County) %>%
  summarise(EEE_Positive_Tests = n()) %>%  # Count the number of EEE positive tests in each group
  arrange(desc(EEE_Positive_Tests))  # Order the results by EEE_Positive_Tests in descending order
